\documentclass[11pt, a4paper, twoside]{article}
\usepackage[T1]{fontenc}
\usepackage{gentium}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\renewcommand{\sfdefault}{qhv}
\renewcommand*\familydefault{\sfdefault}
\usepackage{microtype}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{ulem}
\linespread{1.25}
\usepackage{geometry}
\usepackage{xcolor}
\definecolor{ooni}{RGB}{240, 94, 28}
\geometry{paper=a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm}
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
\fancyhf{}
\fancyfoot[LE,RO]{\footnotesize \bfseries Page | \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}
\pagestyle{plain}
\usepackage[document, bottom, hang, perpage]{ragged2e}
\usepackage{booktabs}
\begin{document}
\begin{minipage}[b]{0.38\textwidth}
  {\Huge \bfseries Wenyao Zhu}\par\vspace{0.7ex}
  {\large \bfseries Ph.\kern0.15emD. candidate}
  \end{minipage}\hfill
  \begin{minipage}[b]{0.6\textwidth}
  \raggedleft
  \footnotesize 1011/8 Airedale St, Auckland Central, Auckland, 1010\kern0.9em\faHome\par
  +64\kern0.3em27\kern0.3em204\kern0.3em1740\kern1em\faPhone\par
  arthz.88@outlook.com\kern1em\scalebox{0.88}{\faEnvelope}\par
  \href{https://www.linkedin.com/in/wenyao-zhu-0b2424120/}{linkedin.com/in/wenyao-zhu-0b2424120}\kern1em \scalebox{1.1}{\faLinkedinSquare}
\end{minipage}\vspace{-1.0ex}
\noindent\rule{\textwidth}{0.7pt}\par\vspace{0.8ex}
To:\par
Recruiting manager,\par
Institute of Environmental Science and Research (ESR),\par
120 Mount Albert Road,\par
Sandringham, Auckland 1025\par
\vspace{4ex}
\textbf{Subject: Expression of interest for 45616 Forensic Data Analytics and Visualisation Engineer at ESR}\par\vspace{2ex}

Dear recruiting manager,\par\vspace{2ex}

I am writing to apply for the role of Forensic Data Analytics and Visualisation Engineer at ESR, which was posted on Seek website: www.seek.co.nz/job/55760999.\par\vspace{2ex}

I am interested in this position, as my experience matches well with ESR's requirements. I have been undertaking a PhD research program at the University of Auckland for the past 3.5 years, which involved intensive use of data analysis skills to solve analytical chemistry, wine science, and sensory science-related problems. Since my PhD research involves the collaboration with a commercial winery (Constellation Brands NZ), I benefited from looking at real-world problems, and providing solutions using research tools. My relevant experience includes establishing a machine learning (artificial neural network) model to differentiate and predict the sensory gradings of wines based on their aroma, as well as differentiating aged wines from fresh wines based on aroma. These findings were also shared with winemakers and readily integrated into their workflows.\par\vspace{2ex}

I mostly used R as the programming language for my data analysis tasks. Besides, I am also familiar with Python, MySQL, Git version control, Markdown and LaTeX for document preparation. In my research, I was solely responsible for collecting and cleansing data, building models, creating plots using ggplot2, and deploying interactive online apps for use by non-experts using R-shiny. I am also fluent in scientific writing and presentation, including two published peer-reviewed journal articles and four presentations (oral and poster) at academic conferences. I have always collaborated effectively with colleagues and worked well in a team with good interpersonal skills.\par\vspace{2ex}

I would appreciate having an opportunity to talk with you more about this position and how my skills would benefit your organisation.\par\vspace{2ex}

Thank you for considering my application, and I look forward to hearing from you soon.\par\vspace{2ex}

Yours Sincerely,\par\vspace{1ex}
Wenyao Zhu
\end{document}
